---
title: "LAB8_ClimateThreats"
author: "Margaux Sleckman"
date: "May 23, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Climate Change Threats 

1. Download the appropriate set of rasters (see Table) and load them into R.

2. Stack the layers and plot them (HINT: if you use the stack function, then you can just call plot once and it will plot all of the layers)

3. Get an idea of the distribution of the data using hist(), cellStats(), or visually by zooming in to different sections of your rasters.

4. Overlay the rasters and perform raster calculations (reclassify, overlay, maybe calc) to create a cumulative threat layer. You may do this however you deem appropriate. Some suggestions:

  A quantile and sum approach, analagous to the above analysis
  A mean threat value per raster cell
  A maximum threat value per raster cell
  A weighted mean
  
  

```{r Packages}


# install.packages(c("raster","rgdal","maps","rgeos","sp","maptools"))
# install.packages(c("dplyr","RColorBrewer"))

library(raster)
library(rgdal)
library(maps)
library(rgeos)
library(sp)
library(maptools)
library(dplyr)
library(RColorBrewer)
library(ggplot2)
library(sf)
```

```{r colors}

cols = rev(colorRampPalette(brewer.pal(11, 'Spectral'))(255)) 

#setting smaller margins for plotting
par(mar=c(2,2,1,1))

```

  
```{r Loading_Data}

setwd("H:/Spring 2018/ESM270-CP/lab8/esm270_lab8")


# Three tif files for this exercise 
acid<-raster("impact_acid.tif")
uv<-raster("impact_uv.tif")
sst<-raster("impact_sst.tif")
all_spp <- raster(("ca_curr_sp_rich.tif"))

plot(all_spp,col=cols)

#Note:Extent are same therefore no resampling needed 
# plot(acid, col=cols); map('world', fill = T, col="grey")

```

```{r Stack_hist}

threats_stack<-stack(acid,uv,sst)
plot(threats_stack, col=cols)
#threats_stack <- resample(threats_stack,method='ngb',progress='text')

#resample
spp_crop <- crop(threats_stack, all_spp) #Crop the threats layer to the same extent at species

#climatethreats_res <- resample(uv, acid, sst, method='ngb',progress='text')
#code above doesn't work

hist(threats_stack)
cellStats(threats_stack,max)

```

```{r UV}

# pre-raster calculation manipulation

uv <- reclassify(uv, rcl=c(-Inf,0,NA))
hist(uv)

uv_cutoff <- quantile(uv, 0.8)

uv_max <- cellStats(uv, max)

rcl_mat_uv <- c(-Inf,uv_cutoff,0,
             uv_cutoff,uv_max,1)

uv_binary <- reclassify(uv, rcl = rcl_mat_uv)

uv_mean <- mean(uv)

```

```{r acid}

# pre-raster calculation manipulation
acid <- reclassify(acid, rcl=c(-Inf,0,NA))
hist(acid)
acid_cutoff <- quantile(acid, 0.8)
acid_max <- cellStats(acid, max)
rcl_mat_acid <- c(-Inf,acid_cutoff,0,
             acid_cutoff,acid_max,1)

acid_binary <- reclassify(acid, rcl = rcl_mat_acid)
acid_mean <- mean(acid)

```

```{r sst}
# pre-raster calculation manipulation
sst <- reclassify(sst, rcl=c(-Inf,0,NA))
hist(sst)
sst_cutoff <- quantile(sst, 0.8)
sst_max <- cellStats(sst, max)

rcl_mat_sst <- c(-Inf, sst_cutoff, 0, 
                  sst_cutoff, sst_max, 1)

sst_binary<-reclassify(sst, rcl=rcl_mat_sst)
sst_mean <- mean(sst)
sst_cutoff <- quantile(sst_mean, 0.8)

```

4. Overlay
```{r Overlay&plot}

climateXY <- function(x,y,z){
  return((x+y+z)/3)
  #climatethreatslayers <- c(x,y,z)
  #return(mean(climatethreatslayers, na.rm=TRUE))
}


#Using quantiles
climatethreats <- overlay(uv, acid, sst, fun=climateXY)
climatethreats_binary <- overlay(uv_binary, acid_binary, sst_binary, fun=climateXY)
#using means 
climatethreats_mean <- overlay(uv_mean, acid_mean, sst_mean, fun=climateXY)
 # --> figure out which is most interesting
#climatethreats_max <- overlay(uv_max, acid_max, sst_max, fun=climateXY)

binary_cols<-c("white","firebrick")

plot(climatethreats)
hist(climatethreats)

plot(climatethreats, main="Distribution of the Mean Cumulative climate change threats on West Coast", sub="variables: uv, acidity, sst", legend=T, ext=extent(-130,-110,20,50)); map('world',fill=T,add=T,col='gray80')

#legend("bottom right", title = "threat value")

```


```{r crop}

threats_crop <- crop(climatethreats, all_spp)
plot(threats_crop)

spp_res1 <- resample(all_spp,threats_crop, method='ngb',progress='text')
plot(spp_res1, col=cols)

threats_spp_stacked<-stack(threats_crop, spp_res1)
plot(threats_spp_stacked, col=cols)

```

```{r spp_parcing}

hist(spp_res1,main="Species Raster Values")

spp_res1 <- reclassify(spp_res1,rcl=c(-Inf,0,NA))
hist(spp_res1,main="Species Raster Values, Zeroes Removed") 

#top 20%
spp_cutoff1 <- quantile(spp_res1,0.75) # Find the value of the 80th percentile
spp_maxVal1 <- cellStats(spp_res1,max) #find the maximum

# Our reclassification matrix. MAKE SURE YOU KNOW WHAT THIS MEANS
rcl_mat1 <- c(-Inf,spp_cutoff1,0,
            spp_cutoff1,spp_maxVal1,1)

#rcl_mat = recl_matrix and it means...from -infinity to spp_cut, this equal to 0. Otherwise 1.
# Reclassify the species layer - call it binary because we should end up with 0 or 1. 
spp_binary1 <- reclassify(spp_res1,rcl=rcl_mat1)

```

```{r PlotingSpeciesBinary}

binary_cols<-c("blue","pink")
#run the two bottom functions TOGETHER: 
plot(spp_binary1, col=binary_cols, legend=F, main="Top 20% of Species Richness");map('world', fill=T, add=T, col='grey')

```

```{r hotspots_CC_spp}

# Function to add x + y

sumCC_spp<-function(x,y){
  return(x+y)
}

# the hotspots 
CC_hotspots<-overlay(spp_binary1, threats_crop, fun=addXY)
plot(CC_hotspots)


#hotspot_cols <- c("white","lightblue","firebrick") #
plot(CC_hotspots,legend=F,main="Hotspots");map('world',fill=T,add=T,col='gray80')


#plot(CC_hotspots,ext=extent(-135,-125,30,35),main= "Climate Change Hotspots",legend=F); map('world',fill=T,add=T,col='gray80')


```

```{r top20CC_threats}



cc_threats_binary <- reclassify(threats_crop, rcl=c(-Inf,quantile(threats_crop, 0.75),0, quantile (threats_crop, 0.75), cellStats(threats_crop, max),1))
plot(cc_threats_binary)

cc_threats_binary2<-reclassify(threats_crop, rcl=c(-Inf,quantile(threats_crop, 0.8),0, quantile (threats_crop, 0.8), cellStats(threats_crop, max),1))
plot(cc_threats_binary2)

```


```{r top25ccthreats_top25spp}

sumCC_spp2<-function(x,y){
  return(x+y)
}

CC_hotspots25<-overlay(cc_threats_binary, spp_binary1, fun=sumCC_spp2)
hotspot_cols_cc<- c("white", "firebrick","gold1")
#par(bg='blue')
plot(CC_hotspots25, main="Overlay of biodiversity hotspots and cumulative climate change threats", legend=F);map('world', fill=T, add=T,col='gray80')

hotspotMap_25 + opts(plot.background=theme_rect(fill="yellow"),panel.background=theme_rect(fill="purple"))
```
```{r}

```

 
```{r random}

threats_cutoff <- quantile(uv,0.8)

threats_stack <- reclassify(threats_stack,rcl=c(-Inf,0,NA))
hist(threats_stack,main="Species Raster Values, Zeroes Removed")

threats_cutoff <- quantile(threats_stack,0.8) # Find the value of the 80th percentile --> i want 20 top threats
threats_max <- cellStats(threats_stack,max) #find the maximum
#threats_cutoff
#threats_max

##DONT REALLY GET THIS function but it runs properly ## 
rcl_mat <- c(-Inf,threats_cutoff,0,
             threats_cutoff,threats_max,1)

# reclassify(threats_crop, rcl=c(-Inf,quantile(threats_crop, 0.8),0, quantile (threats_crop, 0.8), cellStats(threats_crop, max),1))


threats_binary <- reclassify(threats_stack,rcl=rcl_mat)
## GETTING ERROR: "Error: all(rcl[, 2] >= rcl[, 1]) is not TRUE""

# this sets us up for calculating 
```

```{r plots_cumthreats}

plot(threats_binary, col=binary_cols, legend=F, main="Top 20% Climate threats")
map('world', fill=T, add=T, col='grey')

```

