---
title: "LAB8_ClimateThreats"
author: "Margaux Sleckman"
date: "May 23, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Climate Change Threats 

1. Download the appropriate set of rasters (see Table) and load them into R.

2. Stack the layers and plot them (HINT: if you use the stack function, then you can just call plot once and it will plot all of the layers)

3. Get an idea of the distribution of the data using hist(), cellStats(), or visually by zooming in to different sections of your rasters.

4. Overlay the rasters and perform raster calculations (reclassify, overlay, maybe calc) to create a cumulative threat layer. You may do this however you deem appropriate. Some suggestions:

  A quantile and sum approach, analagous to the above analysis
  A mean threat value per raster cell
  A maximum threat value per raster cell
  A weighted mean
  
  

```{r Packages}


# install.packages(c("raster","rgdal","maps","rgeos","sp","maptools"))
# install.packages(c("dplyr","RColorBrewer"))

library(raster)
library(rgdal)
library(maps)
library(rgeos)
library(sp)
library(maptools)
library(dplyr)
library(RColorBrewer)

```

```{r colors}

cols = rev(colorRampPalette(brewer.pal(11, 'Spectral'))(255)) 

#setting smaller margins for plotting
par(mar=c(2,2,1,1))

```

  
```{r Loading_Data}

setwd("H:/Spring 2018/ESM270-CP/lab8/esm270_lab8")


# Three tif files for this exercise 
acid<-raster("impact_acid.tif")
uv<-raster("impact_uv.tif")
sst<-raster("impact_sst.tif")

#Note:Extent are same therefore no resampling needed 

# plot(acid, col=cols); map('world', fill = T, col="grey")

```

```{r Stack_hist}

#
threats_stack<-stack(acid,uv,sst)
plot(threats_stack, col=cols)

#resample

#climatethreats_res <- resample(uv, acid, sst, method='ngb',progress='text')
#code above doesn't work

hist(threats_stack)
cellStats(threats_stack,max)

```

```{r UV}

# pre-raster calculation manipulation
uv_cutoff<-quantile(uv, 0.8)
uv_max<-cellStats(uv, max)
rcl_mat_uv<-c(-Inf,uv_cutoff,0,
             uv_cutoff,uv_max,1)

mean(uv)

uv_binary<-reclassify(uv, rcl = rcl_mat_uv)
uv_binary

uv_mean <- mean(uv)

```

```{r acid}

# pre-raster calculation manipulation
acid_cutoff<-quantile(acid, 0.8)
acid_max<-cellStats(acid, max)
rcl_mat_acid<-c(-Inf,acid_cutoff,0,
             acid_cutoff,acid_max,1)

acid_binary<-reclassify(acid, rcl = rcl_mat_acid)
acid_binary
acid_mean <- mean(acid)

```

```{r sst}
# pre-raster calculation manipulation
sst_cutoff <- quantile(sst, 0.8)
sst_max <- cellStats(sst, max)

rcl_mat_sst <- c(-Inf, sst_cutoff, 0, 
                  sst_cutoff, sst_max, 1)

sst_binary<-reclassify(sst, rcl=rcl_mat_sst)

sst_mean <- mean(sst)
sst_cutoff <- quantile(sst_mean, 0.8)
sst_cutoff
```

4. Overlay
```{r Overlay&plot}

climateXY<-function(x,y,z){
  return(x+y+z)
}

#Using quantiles
climatethreats <- overlay(uv_binary, acid_binary, sst_binary, fun=climateXY)
#using means 
climatethreats <- overlay(uv_mean, acid_mean, sst_mean, fun=climateXY)
 # --> figure out which is most interesting
 
binary_cols<-c("white","firebrick")
plot(climatethreats)

```

```{r random}

threats_cutoff <- quantile(uv,0.8)

threats_stack <- reclassify(threats_stack,rcl=c(-Inf,0,NA))
hist(threats_stack,main="Species Raster Values, Zeroes Removed")

threats_cutoff <- quantile(threats_stack,0.8) # Find the value of the 80th percentile --> i want 20 top threats
threats_max <- cellStats(threats_stack,max) #find the maximum
#threats_cutoff
#threats_max

##DONT REALLY GET THIS function but it runs properly ## 
rcl_mat <- c(-Inf,threats_cutoff,0,
             threats_cutoff,threats_max,1)

# reclassify(threats_crop, rcl=c(-Inf,quantile(threats_crop, 0.8),0, quantile (threats_crop, 0.8), cellStats(threats_crop, max),1))


threats_binary <- reclassify(threats_stack,rcl=rcl_mat)
## GETTING ERROR: "Error: all(rcl[, 2] >= rcl[, 1]) is not TRUE""

# this sets us up for calculating 
```

```{r plots_cumthreats}

plot(threats_binary, col=binary_cols, legend=F, main="Top 20% Climate threats")
map('world', fill=T, add=T, col='grey')

```

